---
title: "Lab 1 - Resampling"
date: "April 8, 2020"
output: 
  html_document:
    toc: true
    toc_float: true
    dev: png
  pdf_document:
    dev: cairo_pdf
    latex_engine: xelatex
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(rio)
library(here)
library(tidyverse)
library(tidymodels)
library(ggthemes)
library(Cairo)
library(tinytex)

theme_set(theme_minimal())

# Reading in the data
train <- read_csv(here::here("train.csv")) %>% 
  as_tibble()
```

# 1. Initial Split

Split the data into a training set and a testing set as two named objects. Produce the class type for the initial split object and the training and test sets.

```{rinitial split}


```

# 2. Proportion

Use code to show the proportion of the train.csv data that went to each of the training and test sets.

```{r proportion}


```

# 3. k-fold cross-validation

Use 10-fold cross-validation to resample the traning data.

```{r kfold}


```

# 4. Use {purrr} to add the following columns to your k-fold CV object:
analysis_n = the n of the analysis set for each fold
assessment_n = the n of the assessment set for each fold
analysis_p = the proportion of the analysis set for each fold
assessment_p = the proportion of the assessment set for each fold
sped_p = the proportion of students receiving special education services (sp_ed_fg) for each fold

```{r purrr}

```

# 5. No common values in k-folds

Please demonstrate that that there are no common values in the id column between Fold01 & Fold02, and Fold09 & Fold10 in your 10-fold cross-validation object.

```{r no common values}


```

# 6. Try to answer these next questions without running similar code on real data.

For the following code vfold_cv(fictional_train, v = 20):

What is the proportion in the analysis set for each fold?
What is the proportion in the assessment set for each fold?

# 7.Monte Carlo

Use Monte Carlo CV to resample the training data with 20 resamples and .30 of each resample reserved for the assessment sets.

```{r monte carlo}

```

# 8. Common values after monte carlo

Please demonstrate that that there are common values in the id column between Resample 8 & Resample 12, and Resample 2 & Resample 20in your MC CV object.

```{r common values}

```

# 9. Bootstrap

You plan on doing bootstrap resampling with a training set with n = 500.
What is the sample size of an analysis set for a given bootstrap resample?
What is the sample size of an assessment set for a given bootstrap resample?

If each row was selected only once for an analysis set:
what would be the size of the analysis set?
and what would be the size of the assessment set?