---
title: "Lab 1 - Resampling"
author: "Katie Denning, Tamara Niella, & Karlena Ochoa"
date: "April 8, 2020"
output: 
  html_document:
    toc: true
    toc_float: true
    dev: png
  pdf_document:
    dev: cairo_pdf
    latex_engine: xelatex
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(rio)
library(here)
library(tidyverse)
library(tidymodels)
library(ggthemes)
library(Cairo)
library(tinytex)

theme_set(theme_minimal())

# Reading in the data
df <- read_csv(here::here("train.csv")) %>% 
  as_tibble()
```

# 1. Initial Split

Split the data into a training set and a testing set as two named objects. 
Produce the class type for the initial split object and the training and test sets.

```{r initial split}

df_split <- initial_split(df)
str(df_split)
  
df_train <- training(df_split)
str(df_train)

df_test <- testing(df_split)
str(df_test)

```

# 2. Proportion

Use code to show the proportion of the train.csv data that went to each of the training and test sets.

```{r proportion}
df_train %>%
  nrow() / nrow(df)
#75% in training set

df_test %>%
  nrow() / nrow(df)
#25% in test df 
```

# 3. k-fold cross-validation

Use 10-fold cross-validation to resample the traning data.

```{r kfold}

train_kfold <- vfold_cv(df_train)

train_kfold

train_kfold$splits[[1]] %>%
  assessment()



```

# 4. Use {purrr} to add the following columns to your k-fold CV object:
analysis_n = the n of the analysis set for each fold
assessment_n = the n of the assessment set for each fold
analysis_p = the proportion of the analysis set for each fold
assessment_p = the proportion of the assessment set for each fold
sped_p = the proportion of students receiving special education services (sp_ed_fg) for each fold

```{r purrr}
kfold_commonvalues <- train_kfold %>%
  mutate(analysis = map(splits, analysis), 
         analysis_n = map_dbl(analysis, nrow), 
         assessment = map(splits, assessment),
         assessment_n = map_dbl(assessment, nrow),
         analysis_p = analysis_n/(analysis_n + assessment_n),
         assessment_p = assessment_n/(analysis_n + assessment_n),
         sped_p = map2_dbl(analysis, analysis_n, ~sum(.x$sp_ed_fg == "Y", na.rm = TRUE)/.y))
kfold_commonvalues
```

# 5. No common values in k-folds

Please demonstrate that that there are no common values in the id column between Fold01 & Fold02, and Fold09 & Fold10 in your 10-fold cross-validation object.(in the Assessment data)

```{r no common values}
#setdiff()
#typeunique

kfold_assess <- kfold_commonvalues %>% 
  select(assessment)

dif_12 <- setdiff(kfold_assess$assessment$`1`[1],kfold_assess$assessment$`2`[1])
dif_12

# length in dif_12 and in assessment_n are equal, meaning that they ar eall different 

dif_910 <- setdiff(kfold_assess$assessment$`9`[1],kfold_assess$assessment$`10`[1])
dif_910

# same for 9 and 10 
```

# 6. Try to answer these next questions without running similar code on real data.

For the following code vfold_cv(fictional_train, v = 20):

What is the proportion in the analysis set for each fold?

1/20 = 5%
What is the proportion in the assessment set for each fold?


```{r}

```

# 7.Monte Carlo

Use Monte Carlo CV to resample the training data with 20 resamples and .30 of each resample reserved for the assessment sets.

```{r monte carlo}
# Running the monte carlo resampling with 20 resamples and .30 prop in assessment/.70 in analysis
df_mc <- mc_cv(df, prop = 7/10, times = 20)
df_mc

# Checking this proportion is correct in split 1, by making sure .70 is in analysis and therefore .30 would be in assessment
analysis(df_mc$splits[[1]]) %>%  nrow / nrow(df_mc$splits[[1]]$data)
```

# 8. Common values after monte carlo
Please demonstrate that that there are common values in the id column between Resample 8 & Resample 12, and Resample 2 & Resample 20in your MC CV object.(in the assesment sets)

```{r common values}

```

# 9. Bootstrap

You plan on doing bootstrap resampling with a training set with n = 500.
What is the sample size of an analysis set for a given bootstrap resample?
What is the sample size of an assessment set for a given bootstrap resample?

If each row was selected only once for an analysis set:
what would be the size of the analysis set?
and what would be the size of the assessment set?